---
format: dashboard
---

#  {.tabset .tabset-pills}

## Daily programme {.tabset}

### Monday

**Epiverse-TRACE perspectives**

**Day 1**: focuses on presenting the project objectives, particularly the planning for its second phase. Attendees will have the opportunity to discuss and review the draft planning document prepared by the PI's. This collaborative approach aims to ensure that the final phase 2 planning document is comprehensive and inclusive.

**Objectives**: - Opening of the summit. - Discuss the implementation of Phase 2 of the Epiverse-TRACE project.

**Expected outcomes**:

-   Gather reviews and feedback to strengthen the proposal for the phase 2 roadmap.

```{r eval=TRUE, echo = FALSE}
day_1_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-11:45",  "12:30-12:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Welcome and registration", "Opening ceremony and launching of phase 2 Epiverse-TRACE project", "coffee break", "Ice breaker", "Planning for phase 2 implementation", "lunch break", "RF/RSE sessions", "Dinner"),
  Speakers = c("-", "Dr Bubacarr Bah, Pr Umberto D'Alessandro, Data.org (TBC), and MoH (TBC)", "", "Banky", "Data.org (TBC)", "", "James and Degoot", "")
)

day_1_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```

### Tuesday

**Sustainability and Inclusivity**

**Day 2** focuses on reflection, strategic planning, inclusivity, and the sustainability of the project.

**Objectives:**

-   Assess how well the project tools currently address diverse populations and settings.
-   Identify gaps in inclusivity (e.g., language barriers, accessibility).
-   Identify opportunities for collaboration from the gaps and needs from phase 1.
-   Expand the scope of our tools to cover public health threats in other parts of the world.
-   Explore the sustainability of the project.

**Expected outcomes:**

-   Identification of:
    -   potential collaborators to fulfill the gaps and needs,
    -   our strengths and weaknesses,
    -   ways of covering more health issues.
-   A strategic roadmap for ensuring the continued relevance and use of our tools post-project.

**Moderators:**

Nuredin Mohammed, Data.org (TBC)

```{r eval=TRUE, echo = FALSE}
day_2_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-12:30", "12:30-13:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Phase 1: lessons learnt/gaps/needs", "Inclisivity of analytics tools in Public Health", "coffee break", "Are epiverse tools inclusive? Where do we fail to achieve inclusiveness?", "Opportunities from the gaps/needs", "lunch break", "Feedback from the activities of the day", "Dinner"),
  Speakers = c("group discussions", "TBC by Nuredin", "", "group discussions", "group discussions", "", "group representatives", "")
)

day_2_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```

### Wednesday

site seeing - include images

### Thursday

**Training and perspectives** focused on designing a data-centered outbreak analytics course

Objectives:

Expected outcomes:

Moderator:

```{r eval=TRUE, echo = FALSE}
day_4_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-12:30", "12:30-13:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Designing outbreak analytics course", "Designing outbreak analytics course", "coffee break", "One health / local outbreaks/ NTDs", "One health / local outbreaks/ NTDs", "lunch break", "RSE session", "Dinner"),
  Speakers = c("", "", "", "", "", "", "", "")
)

day_4_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```

### Friday

**Review** - Describe the day

Objectives:

Expected outcomes:

Moderator:

```{r eval=TRUE, echo = FALSE}
day_5_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-12:30", "12:30-13:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Tools for surveillance", "Tools for surveillance", "coffee break", "Lessons learnt/Gaps/needs", "Lessons learnt/Gaps/needs", "lunch break", "RSE session", "Dinner"),
  Speakers = c("", "", "", "", "", "", "", "")
)

day_5_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```
