---
format: dashboard
---

#  {.tabset .tabset-pills}

## Daily program {.tabset}

### Monday


**Objectives**: 

- Open ceremony and start the official launching of phase 2 of the project
- Discussion of the implementation of Phase 2 of the Epiverse-TRACe project

**Expected outcomes**: 

- Openning remarks from Bubacarr Bah, MRC Director,  Data.org and representative of MoH.
- review and feedback for the proporsal for road-map of phase 2.


```{r eval=TRUE, echo = FALSE}
day_1_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-11:45",  "12:30-12:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Arrival and registration", "opening ceremony and launching of phase 2 Epiverse-TRACE project", "coffee break", "Ice breker", "Planning for phase 2 implementation", "lunch break", "RF/RSE sessions", "Dinner"),
  Speakers = c("-", "Bubacarr, MRC Director, Representative of Data.org, and MOH", "", "Banky", "Representative of Data.org and groups discussion", "", "Representative of RF and RSE teams", "")
)

day_1_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```

### Tuesday

**Inclusivity and Sustainability** - Describe the day

Objectives:

Expected outcomes:

Moderator:

```{r eval=TRUE, echo = FALSE}
day_2_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-12:30", "12:30-13:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("What will happen to the tools when the funding runs out?", "How do we keep the project going?", "coffee break", "Where do we locate the global south?", "Bringing a broader audience", "lunch break", "Establishing alliances", "Dinner"),
  Speakers = c("", "", "", "", "", "", "", "")
)

day_2_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```

### Wednesday

site seeing - include images

### Thursday

**Training and perspectives** - Describe the day

Objectives:

Expected outcomes:

Moderator:

```{r eval=TRUE, echo = FALSE}
day_4_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-12:30", "12:30-13:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Designing outbreak analytics course", "Designing outbreak analytics course", "coffee break", "One health / local outbreaks/ NTDs", "One health / local outbreaks/ NTDs", "lunch break", "RSE session", "Dinner"),
  Speakers = c("", "", "", "", "", "", "", "")
)

day_4_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```

### Friday

**Review** - Describe the day

Objectives:

Expected outcomes:

Moderator:

```{r eval=TRUE, echo = FALSE}
day_5_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-12:30", "12:30-13:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Tools for surveillance", "Tools for surveillance", "coffee break", "Lessons learnt/Gaps/needs", "Lessons learnt/Gaps/needs", "lunch break", "RSE session", "Dinner"),
  Speakers = c("", "", "", "", "", "", "", "")
)

day_5_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```
