---
format: dashboard
---

#  {.tabset .tabset-pills}

## Daily program {.tabset}

### Monday

**Epiverse-TRACE perspectives**

Day 1 aims at presenting the project perspectives, specially the planning of its second phase. Attendees will discuss and review the planning drafted by the PIs. This way, we expect to achieve the inclusiveness of the ultimate phase 2 planning document.


**Objectives**: 

- Discuss the implementation of Phase 2 of the Epiverse-TRACE project.

**Expected outcomes**: 

- Gathering reviews and feedback to reinforce the proposal for road-map of phase 2.


```{r eval=TRUE, echo = FALSE}
day_1_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-11:45",  "12:30-12:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Welcome and registration", "opening ceremony and launching of phase 2 Epiverse-TRACE project", "coffee break", "Ice breaker", "Planning for phase 2 implementation", "lunch break", "RF/RSE sessions", "Dinner"),
  Speakers = c("-", "Dr Bubacarr Bah, Pr Umberto D'Alessandro, Data.org (TBC), and MoH (TBC)", "", "Banky", "Data.org (TBC)", "", "James and Degoot", "")
)

day_1_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```

### Tuesday

**Sustainability and Inclusivity**

Day 2 aims at evaluating phase 1 of the project and discussing the ways to keep the project going, while accounting for the health concerns in the global south. 

**Objectives:**

* Determine the lessons learnt in phase 1.
* Identify opportunities for collaboration from the gaps and needs from phase 1.
* Expand the scope of our tools to cover public health threats in other parts of the world.
* Determine the “fate” of our tools when the project runs out.

**Expected outcomes:**

* Identification of:
    - potential collaborators to fulfill the gaps and needs,
    - our strengths and weaknesses,
    - ways of covering more health issues.
* A strategic plan for keeping the project and tools alive

**Moderators:**

Nuredin Mohammed,
Data.org (TBC)

```{r eval=TRUE, echo = FALSE}
day_2_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-12:30", "12:30-13:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Phase 1: lessons learnt/gaps/needs", "Inclisivity of analytics tools in Public Health", "coffee break", "Are epiverse tools inclusive? Where do we fail to achieve inclusiveness?", "Opportunities from the gaps/needs", "lunch break", "Feedback from the activities of the day", "Dinner"),
  Speakers = c("group discussions", "TBC by Nuredin", "", "group discussions", "group discussions", "", "group representatives", "")
)

day_2_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```

### Wednesday

site seeing - include images

### Thursday

**Training and perspectives** - Describe the day

Objectives:

Expected outcomes:

Moderator:

```{r eval=TRUE, echo = FALSE}
day_4_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-12:30", "12:30-13:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Designing outbreak analytics course", "Designing outbreak analytics course", "coffee break", "One health / local outbreaks/ NTDs", "One health / local outbreaks/ NTDs", "lunch break", "RSE session", "Dinner"),
  Speakers = c("", "", "", "", "", "", "", "")
)

day_4_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```

### Friday

**Review** - Describe the day

Objectives:

Expected outcomes:

Moderator:

```{r eval=TRUE, echo = FALSE}
day_5_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-12:30", "12:30-13:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Tools for surveillance", "Tools for surveillance", "coffee break", "Lessons learnt/Gaps/needs", "Lessons learnt/Gaps/needs", "lunch break", "RSE session", "Dinner"),
  Speakers = c("", "", "", "", "", "", "", "")
)

day_5_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```
